SMT-Based Generation of Symbolic Automata \thanks{This work was partially funded by the Associated Team FM4CPS between INRIA and ECNU, Shanghai}

### 2019-11-19 2017-Xudong-SMT/ActaInformatica.tex
final versino ??

\newcommand{\TODO}[1]{\textcolor{red}{\textbf{[TODO:#1]}}}
%\newcommand{\TODO}[1]{}
\newcommand{\NOTE}[1]{\textcolor{blue}{\textbf{[NOTE:#1]}}}
\newcommand{\ERIC}[1]{\textcolor{blue}{#1}}
\newcommand{\OTvar}{\texttt}
\newcommand{\OTland}{\;\land\ }
\definecolor{airforceblue}{rgb}{0.26, 0.44, 0.56}
\newcommand{\QIN}[1]{\textcolor{airforceblue}{#1}}
\newcommand{\coloncolon}{{:\hspace{-.2ex}:}}
\definecolor{darkgreen}{rgb}{0.2, 0.55, 0.2}
\newcommand{\Simon}[1]{\textcolor{darkgreen}{#1}}

@@

\newcommand{\YX}[1]{{\color{red}#1}}

@@

\st{But the interaction feature in architectures does not handle
data-sensitive interaction constraints. Using an encoding of
architectures, extended with data-dependent interactions, into open
pNets was an interesting alternative to a direct extension to the
architecture semantics.}

@@

We validate the approach on \Simon{a larger example}\st{two larger examples}, 
based on a BIP architecture taken from an earlier nanosatellite case
study~\cite{CubETH-case-study}.  \Simon{This example shows that
open-automata-based semantics can be instrumental in verifying the
properties enforced by the architectures through an encoding into open
pNets.
In order to evaluate the potential
%
of our approach to scale to larger systems, we also apply the proposed
techniques to a BIP architecture obtained by combining two instances
of the Failure Monitor architecture.  Our results show that, even
though, the performance of the smart algorithm degrades more than
linearly, execution times remain reasonably small.  It should be noted
that the aim of our approach, particularly in the case of BIP
architectures, is to allow symbolic verification of design patterns to
show that they do impose corresponding properties. Safety of the system is obtained compositionally, whereas liveness is verified by checking \emph{pair-wise} non-interference.
%
}\st{We also show how such architectures
can be composed, and how our approach scales.
This example shows that
open-automata-based semantics can be instrumental in verifying the
properties enforced by the architectures through an encoding into open
pNets.
We also compare the practical performances of the two algorithms and
show the benefit gained using the smart approach.}

@@

>>>>

\newcommand{\TODO}[1]{\textcolor{red}{\textbf{[TODO:#1]}}}
%\newcommand{\TODO}[1]{}
\newcommand{\NOTE}[1]{\textcolor{blue}{\textbf{[NOTE:#1]}}}
\newcommand{\OTvar}{\texttt}
\newcommand{\OTland}{\;\land\ }
\definecolor{airforceblue}{rgb}{0.26, 0.44, 0.56}
\newcommand{\coloncolon}{{:\hspace{-.2ex}:}}
\definecolor{darkgreen}{rgb}{0.2, 0.55, 0.2}
%\newcommand{\Simon}[1]{\textcolor{darkgreen}{#1}}
%\newcommand{\ERIC}[1]{\textcolor{blue}{#1}}
%\newcommand{\QIN}[1]{\textcolor{airforceblue}{#1}}
%\newcommand{\YX}[1]{{\color{red}#1}}
\newcommand{\Simon}[1]{{#1}}
\newcommand{\ERIC}[1]{{#1}}
\newcommand{\QIN}[1]{{#1}}
\newcommand{\YX}[1]{{#1}}

@@

@@

%% \st{But the interaction feature in architectures does not handle
%% data-sensitive interaction constraints. Using an encoding of
%% architectures, extended with data-dependent interactions, into open
%% pNets was an interesting alternative to a direct extension to the
%% architecture semantics.}

@@

We validate the approach on \Simon{a larger example},%\st{two larger examples}, 
based on a BIP architecture taken from an earlier nanosatellite case
study~\cite{CubETH-case-study}.  \Simon{This example shows that
open-automata-based semantics can be instrumental in verifying the
properties enforced by the architectures through an encoding into open
pNets.
In order to evaluate the potential
%
of our approach to scale to larger systems, we also apply the proposed
techniques to a BIP architecture obtained by combining two instances
of the Failure Monitor architecture.  Our results show that, even
though, the performance of the smart algorithm degrades more than
linearly, execution times remain reasonably small.  It should be noted
that the aim of our approach, particularly in the case of BIP
architectures, is to allow symbolic verification of design patterns to
show that they do impose corresponding properties. Safety of the system is obtained compositionally, whereas liveness is verified by checking \emph{pair-wise} non-interference. In both cases, the main characteristic of the approach is compsitionality, so we can compute the behavior and analyse the properties on \emph{small open systems}, and use these properties independently when composing bigger systems.
%
}
%% \st{We also show how such architectures
%% can be composed, and how our approach scales.
%% This example shows that
%% open-automata-based semantics can be instrumental in verifying the
%% properties enforced by the architectures through an encoding into open
%% pNets.
%% We also compare the practical performances of the two algorithms and
%% show the benefit gained using the smart approach.}

@@

The reader may notice that the structure of OTs produced by these rules is richer than the one from the definitions in Section \ref{def:OpenTransitions}, as they contain information about the leaves transitions in each OT. This is also the case in the implementation, and provides us with tracability and debugging features in the tool.
